A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Discussion improvement

In our experiments, we found that for simple problems, the cost of
communication between containers will increase the total time of execution,
however, we believe that the opposite must also be true: for complex problems,
distributing the work on multiple resources must reduce time, making the
communication cost negligible.

>>>>

We must acknowledge the performance time of the DEAP library is highly
efficient and short, due in part because the processing work execution is on a
single processor with multiple cores, where the communication time is nearly
non-existent. In contrast, our algorithm implementation requires a minimum of
five containers and a message queue server. Even though the container work has
proven to be very effective and efficient [X], we must consider some time was
added to our experiments by the minimal delays (in the thousands of a second
magnitude) we used to keep the process execution relatively random, to mimic
how the life-cycle stages work in nature. As future work, we could test the
Life-Cycle algorithm behavior by eliminating all remaining delays.

In our experiments, we found that when solving simple problems, the cost of
communication between containers can become a factor to increase the total
performance time, even though, we believe that the opposite must also be true.
When solving complex problems, distributing the work on multiple resources
should reduce throughput time, making the communication cost negligible.
